% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2007-2014 Todd C. Miller <Todd.Miller@sudo.ws> http://www.sudo.ws/todd
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\usepackage{enumitem}
\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large Loh Sheng Yang, Michael}  & michaellohsy@gmail.com\\
Blk 341 Hougang Ave 7, Singapore 530341 & \href{https://www.linkedin.com/in/michael-loh-sy}{LinkedIn} \\
+65 97986543 & \href{https://github.com/michaellohsy}{GitHub} \\
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Summary}

\begin{description}[style=unboxed,leftmargin=0.2cm]
\item Highly motivated software engineer with thorough hands-on experience working on different technologies and stacks. A team player with great communication skills who possesses excellent trouble shooting expertise. Adept in machine learning and data analysis with a passion for learning new technologies.
\end{description}

\resheading{Education}
\begin{itemize}
\item
	\ressubheading{National University of Singapore (NUS)}{Singapore}{Bachelor in Computer Engineering}{Aug. 2009 - May. 2013}
\item
	\ressubheading{University of California, Berkeley, San Francisco}{USA}{Summer Exchange}{May. 2011 - July. 2011}

\end{itemize}

\resheading{Work Experience}
\begin{itemize}
\item
	\ressubheading{Plunify}{Singapore}{Senior Software Engineer}{May 2016- Present}
	\begin{itemize}
	    \resitem{Main developer for Web and Cloud platform involving new architecture and legacy code.}
	    \begin{itemize}
			\resitem{Launching of AWS cloud instances for FPGA chip optimization.}
			\resitem{Developed credits and cloud instance management platform.}
			\resitem{Integrated payment and OAuth services for web application.}
	    \end{itemize}
	    \resitem{Developed and integrated desktop GUI application with cloud platform.}
	    \resitem{Optimized code and database queries resulting in 90\% speed-up.}
		\resitem{Created machine learning algorithms which reduced FPGA chip optimization times by 20\%.}
		\resitem{Performed data visualization and analysis of FPGA data to gain insights into FPGA optimization.}
	\end{itemize}
\item
	\ressubheading{Bioinformatics Institute}{Singapore}{Software Developer}{August 2013 - April 2016}
	\begin{itemize}
		\resitem{Implemented a novel microscopy screening algorithm and helped reduce acquisition time by 40\%.}
		\resitem{Performed image registration on biomedical image slices for drug analysis.}
		\resitem{Developed image processing algorithms and	 software for fly specie detection with 99\% accuracy.}
		\resitem{Analysed and provided machine learning solutions for FPGA timing and optimization problems.}
	\end{itemize}
\item
	\ressubheading{Citibank}{Singapore}{Intern}{January 2012 - June 2012}
	\begin{itemize}
		\resitem{Performed source code migration from CVS to Perforce.}
		\resitem{Tested electronic trading simulators and provided feedback to vendors.}
		%\resitem{Set up and deployed an electronic trading simulator.}
	\end{itemize}
\end{itemize}

\resheading{Skills}

\begin{description}
\item[Languages:]
Java, C{}\verb!++!, Python, R, PHP, SQL, HTML, CSS, Javascript, Ansible
\item[Libraries/Frameworks:]
QT, Tensorflow, Keras, JQuery, AngularJS, Bootstrap, OpenCV, ImageJ
\end{description}

\resheading{Publications}

\begin{itemize}
  \item \small{\href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5490177/pdf/12859_2017_Article_1720.pdf}{Loh, S. Y. M., Ogawa, Y., Kawana, S., Tamura, K., \& Lee, H. K. (2017).}} \\ \scriptsize{Semi-automated quantitative drosophila wings measurements. \textit{BMC Bioinformatics, 18}(319). doi:10.1186/s12859-017-1720-y }
  \item \small{\href{https://www.nature.com/eye/journal/v31/n4/full/eye2016267a.html}{Nongpiur, M. E., Atalay, E., Gong, T., Loh, S. Y. M., Lee, H. K., He, M., Perera, S., \& Aung, T. (2016).}} \\  \scriptsize{Anterior segment imaging-based subdivision of subjects with primary angle closure glaucoma. \textit{Eye, 31}, 572-577. doi:10.1038/eye.2016.267}
  \item \small{\href{http://onlinelibrary.wiley.com/doi/10.1002/cyto.a.22909/abstract}{Bougen-Zhukov, N., Loh, S. Y. M., Lee. H. K., \& Loo, L. (2017).}} \\ \scriptsize{Large-scale image-based screening and profiling of cellular phenotypes. \textit{Cytometry Part A, 91}, 115-125. doi:10.1002/cyto.a.22909}
\end{itemize}

\end{document}
